Neural Neural Textures Make Sim2Real Consistent

### 2022-06-24 CORL/example.tex
Added neural neural texture paragraph

>>>>

% The three main technical contributions of this paper are our neural neural texture, and two separately sufficient surface consistency losses.
One of the main contributions of this paper is our `neural neural texture'.
Inspired by previous works, TRITON uses raster-based neural textures to create realistic images \cite{deferred_neural_rendering,surgical_video_translation}.
Unlike those works however, we do not use a pixel-based neural texture. Instead, we use what we call a ``neural neural texture'': a continuous implicit pixelless parametric texture represented by a neural netork using fourier features \cite{fourier_feature_networks} that takes in 2d UV coordinates and outputs colors.
